Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-03 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Weibul fit
@JJ please check, Paco there is a missing reference.

\begin{table}
  \small
  \caption{ After a week of the announcement the total number of volunteers, 
  nodes and edges in the graph and analytics URLs}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l l l l}
    \hline\noalign{\smallskip}
     Deployment &  Users &  Nodes &  Edges & URL \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & 53 &  595   & 2220  & goo.gl/jLis4Q.info \\ \hline
    G   & 54 &  648   & 2596  & goo.gl/jqjNy5.info \\ \hline
    GG  & 68 &        & 3594  & goo.gl/J8TCe1.info \\ \hline
    \end{tabular}
\end{table}

After a week of the announcement the total number of volunteers,nodes and edges 
in the graph, for for each experiment is shown in table \ref{tab:urls}.
Moreover, the total number of evaluated phenotypes for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} in blue. Users are ranked by the 
number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale. 
Results  show that those users with higher level of participation in deployments B and G, had
about the same behavior, but the difference came with users with medium level of participation,
in this case participants where more engaged in deployment G. When comparing all the experiments
the deployment GG had the higher number of participation in users of all levels.

@@

\section{Case Study: EvoDraw-Kinect}
The EvoDraw installation is an IEA in which viewers interact with animations by simply
looking at them. Drawings emerge from animations scripted in the Processing 
language, and each is configured by a list of parameters represented by their
chromosome. To start the evolutionary cycle, first a population of animations is 
randomly generated and stored in a container server called EvoSpace. 
Once the population is active,  client computers remove animations from the evospace 
server to be presented in a monitor one at a time. After a certain amount of time, 
animations are put back to the server along with information generated from the interaction.
To continue, another is again removed and presented to viewers. An important feature 
is that once an animation is removed from the server, no other client can remove it, 
until the client that remove it puts the animation back, this means that any
animation is been shown only on one client at a given time. This cycle continues until there
is enough interactions to create a new generation of animations.

In the previous version of this system \citep{garcia2013evospace} 
viewers directly assigned a rating to each animation via a web page; in this work, viewers
only need to see the animations on different monitors, but this time they can look at them 
or not, just like the paintings inside a gallery. In order to assign a fitness value to 
each animation and thus  enabling the EA the selection of the more interesting animations, 
a natural user interface device (Kinect sensor for Xbox One)
is used for facial tracking. The sensor can track up to 6 persons at once and  
it provides a basic set of information for every face: where the face is, where it is looking, 
basic expressive information, and if the face has glasses, which are used to compute the
attention received by each simulation. Each animation is 
presented several times in a single generation and the best are always passed to the next, 
with its fitness recomputed. To generate the new population GA operators
are applied to the population. One or more client computers are needed in order to run the 
installation, each needing a Kinect sensor to keep track of viewers.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/kinect.png}
    \caption{EvoDraw Instalation on Alife XV.}
    \label{fig:kinect}
\end{figure}

@@

XYZ is a collective artwork generated by means of the Unplugged version of the Evolutionary Algorithm.  While in the previous cases software tools are in charge of running the EA and users collaborate evaluating fitness quality, the software tool in XYZ is only in charge of storing digital versions of the works produced by the team of artists, who are really in charge of applying every step of the evolutionary algorithm.

@@

Artists resort to i-EvoSpace as the tool allowing them to store the paintings, deciding their preferred ones from the previous generation, as well as describing the reasons for their selections, mutation and crossover operations applied.  The tool is also in charge of generating statistics, computing \textit{elitism}, thus adding the most selected work to the next generation, etc.

>>>>

\begin{table}
  \small
  \caption{ After a week of the announcement the total number of volunteers, 
  nodes and edges in the graph and analytics URLs}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l l l l}
    \hline\noalign{\smallskip}
     Deployment &  Users &  Nodes &  Edges & URL \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & 53 &  595   & 2220  & goo.gl/jLis4Q.info \\ \hline
    G   & 54 &  648   & 2596  & goo.gl/jqjNy5.info \\ \hline
    GG  & 68 &  932   & 3594  & goo.gl/J8TCe1.info \\ \hline
    \end{tabular}
\end{table}

Table \ref{tab:urls} shows the total number of volunteers, nodes and edges 
in the graph after each experiment. Moreover, the total number of evaluated 
phenotypes for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} where users are ranked by the 
number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale. Results show that when 
considering deployments B and G, the difference came with users with a medium level of participation.
When comparing all the experiments the deployment GG had the higher number of participation in users of all levels.

@@

Moreover, modeling the performance of an C-IEC system
involves understanding its dynamics. Previous works on browser-based
volunteer computing have used metrics basic such as: 
the number of users or the time spent by every one in the
computation \cite{DBLP:journals/gpem/LaredoBGVAGF14, 2016arXiv160101607M}. 
While works on other platforms such as SETI@home
\cite{javadi2009mining} have found that the Weibull, log-normal, and
Gamma distributions where viable modeles of the  
the availability of computing resources in several clusters.
This is in concordance with the results obtained in \cite{agajaj}, and also
browser-based volunteer evolutionary systems like NodIO \cite{DBLP:conf/gecco/MereloCGCRV16}.
The shape of those distributions is a skewed bell
with more resources in the {\em low} areas than in the high areas:
there are many users that give a small amount of cycles, while there
are just a few that give many cycles.

In orther to assess if C-IEC follow the same pattern, even when
using gamification techniques, participation was fittted to a 
Weibull distribution, results in figures \ref{fig:w1}--\ref{fig:w3}  show that 
the same pattern appears in this case study.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3in]{img/weibull_1.png}
    \caption{Experiment 1. Weibull Fit}
    \label{fig:w1}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3in]{img/weibull_2.png}
    \caption{Experiment 2. Weibull Fit}
    \label{fig:w2}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3in]{img/weibull_3.png}
    \caption{Experiment 3. Weibull Fit}
    \label{fig:w3}
\end{figure}

\section{Case Study: EvoDraw-Kinect}

A variation of the previous application is The EvoDraw installation , using the same
framework but with a different form of interaction. Humans interact with the animations 
by simply looking at them. Again the population is stored in the EvoSpace container and
client computers remove animations from the EvoSpace to be presented in a display one at a time. 
After a certain amount of time,  animations are put back to the server along with information 
generated from the interaction. To continue, another is again removed and presented to viewers. 
An important feature is that once an animation is removed from the server, no other client can remove it, 
until the client that remove it puts the animation back, this means that any
animation is been shown only on one client at a given time. This cycle continues until there
is enough interactions to create a new generation of animations.

In order to assign a fitness value to each animation and thus enabling the EA the selection of the more interesting animations, a natural user interface device (Kinect sensor for Xbox One)
is used for facial tracking. Each animation is 
presented several times in a single generation and the best are always passed to the next, 
with its fitness recomputed. To generate the new population the same operators as the previous case study
are applied to the population.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/kinect.png}
    \caption{EvoDraw Instalation on Alife XV Cancun Mexico.}
    \label{fig:kinect}
\end{figure}

In this instalation the components of the framework used where the EvoSpace and the Evolutionary Algorithm.
Information from users was limited to a stream of readings from the sensor.

@@

XYZ is a collective artwork generated by means of the Unplugged version of the Evolutionary Algorithm.
While in the previous cases software tools are in charge of running the EA and users collaborate evaluating
fitness quality, the sframework in XYZ is only in charge of storing digital versions of the works produced 
by the team of artists, who are really in charge of applying every step of the evolutionary algorithm. In 
this case only the relations are stored, and a basic user profile.

@@

Artists resort to framework as the tool allowing them to store the paintings, deciding their preferred ones from the
previous generation, as well as describing the reasons for their selections, mutation and crossover operations applied.
The tool is also in charge of generating statistics, computing \textit{elitism}, thus adding the most selected work to 
the next generation, etc.
